{\bf Intrusion Detection through Provenance-Based Histograms}

### 2013-11-22 writeup/paper.tex
Added Table

\subsection{Statistical Data}
\subsection{KDE Predictions}
TODO:
true positives.
false positives.
graphs?

>>>>

\subsection{Statistical Data}
Table 1 summarizes some of the preliminary results we have generated. Here we have included, for each statistic and test, the average over the "normal" nodes, the observed value for the "test" node, and the KDE probability output for that value. We have chosen four metrics that provided a statistically significant result. The other statistics failed to be as powerful (see Table 2 XXX).
% from http://hhh123.wordpress.com/2008/08/13/latex-table-across-two-columns/
\begin{center}
\begin{table*}[ht]
{\small
  \begin{tabular}{| l | l | l | l |}
    \hline
    metric & hello & mcrypt & gcc \\ \hline
     \# forked processes & 0.0 | 1 | 0.108 & 0.0 | 1 | 0.107 & 0.9 | 9 | 0.408 \\ \hline
     \# input files & 0.5 | 0 | 0.453 & 0.5 | 0 | 0.453 & 0.5 | 1 | 0.107 \\ \hline
     \# ouptut files & 0.5 | 1 | 0.453 & 0.5 | 1 | 0.453 & 0.0 | 3 | 0.000 \\ \hline
    Opsahl centrality & 1.791 | 2.83 | 0.252 & 1.250 | 4.867 | 0.000 & 2.793 | 7.415 | 0.024 \\
    \hline
  \end{tabular}
}
\hfill{}
\caption{average over good | test node value | kde(test node is normal)
}
\label{tb:tablename}
\end{table*}
\end{center}
\subsection{KDE Predictions}
TODO:
true positives.
false positives.
graphs?
